### 2009-01-30 doc/sec/papers/CCGRID09/Sec_paper.tex
Moving papers to dedicated places

@@

\liststyleLi
\begin{enumerate}
\item[] {\centering
1. Introduction
\par}
\end{enumerate}
\ \ \ \ Grid provides the technology for wide-scale, cross domains
collaboration where the users work on resources and sharing data which
are distributed across domains. This kind of collaboration is called
virtual organization (VO)[1]. The resources that contribute to the VO
could come from independent administrative domains, and even require
different security approaches for control the access to themselves
because different middlerwares are used as platform. The same
heterogeneous situation applies to users who need to access the VO,
because users holding one kind of credential could need to travel
through multiple resources with different security approaches. To solve
the above issues, the Grid middlewares should provide the following
ability:

\liststyleLii
\begin{itemize}
\item The user which participates the VO should be able to access data
and resources without being required to constantly do authentication at
each resource or data; 
\item The VO should be able to easily manage the privileges or
memberships of the users; 
\item The VO together with its resources should be able to easily manage
the authorization, given the condition that the resources are owned by
different administrative domains.
\end{itemize}
\ \ \ \ In grid community, Grid Security Infrastructure (GSI)[2] is the
\textit{de facto} for authentication and \ transport level
communication, which builds on Public Key Infrastructure (PKI), an
architecture based on X.509 public key certificate. GSI implements some
enhancement (such as certificate delegation) based on standard SSL/TLS
protocol. Mutual authentication is required by GSI, and is the default
configuration for GSI based grid deployment. The X.509 certificates are
required for both the client and service sides in order to achieve
mutual authentication. The X.509 certificates are issued by trusted
third parties called certificate authorities (CA), and then CAs
constitute trust federation and guarantee two different X.509
certificates from different CAs can accomplish authentication to each
other. So in the GSI based Grid system, if a user would access Grid
system, he/she should own a X.509 certificate which is issued by a CA
that is trusted by other entity.

\ \ \ \ In terms of the virtual organization issues mentioned earlier,
GSI and some other related solutions like Virtual Organization
Management Service (VOMS) [3] have partly solved them in some sense.
The identity delegation and X.509 proxy certificate initiated by GSI
can achieve single sign-on, so that the need to re-enter the
user{\textquotesingle}s pass phrase for authentication can be avoided
by creating the proxy certificate. \ As the most successful Grid
authorization model, VOMS adopts Attribute Certificate[4] approach.
Attribute Certificate is signed by VOMS server and then binded to proxy
certificates by client, \ and attributes certificate includes the VO
memberships which is associated with the proxy
certificate{\textquotesingle}s identity. Eventually the resources can
make access control decision based on parsing the VO membership
attributes from the homogeneous attribute certificate.

@@

\liststyleLiii
\begin{itemize}
\item The GSS API based confidential communication has also not been
adopted by Web Service implementation.
\item The Attribute Certificate has not been adopted by any Web Service
implementation at all.
\item Web Service implementations commonly use the Web Services
Security(WS-Security)[8], Security Assertion Markup Languages
(SAML)[9], and standard SSL/TLS as well as standard X.509 certificate
when considering security, which make them impossible to interoperate
with the GSI based grid middlewares.
\item Finally, identity delegation is a good solution for user or
user{\textquotesingle}s delegatee (on behalf of the user) to
move/travel from one resource to another resource. But since the
identity delegation has been completely coupled with the GSI
confidential communication process, it is not possible for the existing
identity delegation solution to be used by Web Service applications.
\end{itemize}
\ \ \ \ Moreover, the grid security solutions require each user to
possess a X.509 certificate. But the process to get a certificate may
take quite long time, since the requester needs to be checked and
approved by the Registration Authority (RA) and then the Certificate
Authority (CA) can issue the certificate according to the approval from
RA. Meanwhile the process to use the certificate is also not so easy
for the wider less-IT focused research community to deal with, since
the user need to generate the proxy certificate by using the grid
specific command lines, such as \textit{grid-proxy-init}, and
\textit{voms-proxy-init}. On the other hand, users could often have
some local community/institutional credentials such as
username/passwords to which users are more familiar. Enabling users to
use their own community credential instead of the X.509 certificate to
access grid is a promising solution to make the Grid more easily
accessible.

@@

\ \ \ \ ARC(Advanced Resource Connector) is an open source Grid
middleware solution released under Apache license. ARC middleware
initially aimed at developing self-organized, fault-tolerant,
non-intrusive, easy-manageable Grid middleware [10]. \ Now \ the
classic version of ARC provides Grid services for job submission and
management, resource characterization, resource aggregation and
discovery, basic data management, integration of grid security
solution, etc. Classic ARC has been deployed and used in production
environment, and been one of the widely deployed Grid middlewares in
Europe.

\ \ \ \ The new generation of ARC is developed by KnowARC project [11],
based on the functionality and capabilities of the classic ARC
middleware. It aims at implementing a Web Service oriented middleware
which will provide higher levels of resource and user abstraction
through well-defined web service interface [12] in order to provide
interoperability with other service-based Grid middlewares, as well as
other Web Service compatible applications.

@@

\begin{center}
\includegraphics[width=3.7465in,height=3.3764in]{Secpaper-img1.png}
\end{center}

@@

\ \ \ \ HED contains a framework for implementing and enforcing
authentication and authorization. Each MCC or Service has a common
interface for implementing various authentication and authorization
functionality. Each functionality can be implemented as a pluggable and
configurable component (plug-ins) called \textit{SecHandler} which is
C++ class and provides method for processing message that travels
through MCC or Service. Each MCC or Service is usually configured with
two queues of \textit{SecHandler} -- one for incoming message and one
for outgoing message respectively. All \textit{SecHandler} components
attached to the queue are executed sequentially. If any of them fails,
message processing fails as well. In Figure 1, the
{\textquotedblleft}AuthZ{\textquotedblright} and
{\textquotedblleft}AuthN{\textquotedblright} sub-modules inside MCCs
and Services are examples of \textit{SecHandler}.

As explained above, HED is supposed to act as a Web/Grid Service
container, but on the client side, from implementation perspective,
there is similar architecture implemented for processing messages from
different protocols and handling security functionality, also there is
a specific application programming interface (API) for developers to
easily write Web Service client code.

@@

\liststyleLiv
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standard-compatible community authentication mechanism from
Shibboleth [14] Identity Provider software when users authenticate
against Grid services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificates for users by using the community
authentication, in order to interoperate with services that depend on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on characteristic.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item \textit{SAML token delegation service} -{}-{}- to process the WS
Security SAML token in order to provide single sign-on for SOAP message
level authentication.
\end{itemize}
3.1 Community based authentication for Grid by utilizing Shibboleth
Identity Provider

@@

\ \ \ \ Shibboleth provides cross-domain single sign-on and
attribute-based authorization while preserving user privacy. It is
based on the OASIS Security Assertion Markup Language (SAML),
especially the \ new version of Shibboleth supports SAML 2.0
specification. For authentication, the main SAML profile that
Shibboleth implements is the SAML2.0 web browser SSO profile, which
\ define two functional components, an Identity Provider and a Service
Provider. The Identity Provider (IdP) is responsible for creating,
maintaining, and managing user identity, while the Service Provider
(SP) is responsible for controlling access to services and resources by
using the SAML assertion produced and issued by IdP upon request. In
order to discover which home community does a user from, Shibboleth
specifies an optional third component called {\textquotedblleft}Where
Are You From?{\textquotedblright} (WAYF) service to aid in the process
of IdP discovery, and this IdP discovery process is also standardized
and \ defined in SAML 2.0 specification and called as
{\textquotedblleft}Identity Profile Discovery
Profile{\textquotedblright}.

@@

\liststyleLv
\begin{enumerate}
\item The client uses the user agent interface to launches a http
request including the IdP name (to which the user belongs) to the
service side. The endpoint of the SP service is the same as that of the
other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that user who would access
the target services should better know where is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata format defined in Shibboleth) and gets the location
of the single sign-on service (hosted in IdP) and also the location of
assertion consuming service (hosted in this SP itself) in order to
compose the SAML {\textless}\textit{samlp:AuthnRequest}{\textgreater}
message. Then SP Service issues this
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message by using
its own X.509 certificate (Note in the SAML SSO profile, certificate is
still needed by IdP and SP) and sends back to user agent.
\item User agent sends the
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message to
Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile.
Shibboleth IdP implementation chooses some login handler for
authentication. The current user agent implementation is compatible to
\textit{Username/Password} login handler of Shibboleth IdP. Through the
http protocol, user agent will feed IdP with the username/password
which has been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, and decrypts
and stores the SAML assertion into session/connection context. The SAML
assertion includes the
{\textless}\textit{saml:AuthnStatement}{\textgreater} and
{\textless}\textit{saml:AttributeStatement}{\textgreater}.
\item The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.
\item The Grid/Web Service checks the
{\textless}\textit{saml:AuthnStatement}{\textgreater} from the session
context to see if the session is still valid through the
\textit{SecHandler} called {\textquotedblleft}\textit{SAML
SecHandler}{\textquotedblright}. If valid, service handles the service
processing and returns the response to WS client. Note that service
requires that WS client is from the same connection as the one on which
user agent contact SP service, in order to guarantee that the validity
of SSO profile result effects the WS client/Web Service interaction.
\end{enumerate}
\ \ \ \ The SP service and other functional service(s) are hosted by the
same container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for client side
so that SP and IdP can authenticate themselves to the client. As
required by SAML2.0 profile, the SP and IdP should have trust
relationship to each other.

@@

Moreover, even though the implementation is based on ARC middlerware,
the idea can be adopted by other grid middlewares if they only require
server authentication instead of mutual authentication.

@@

\ \ \ \ Since the lifetime of the short lived credential is normally
short, it is not a must to protect the private key by pass-phrase. As
illustrated in step a and step b in Figure 3, if the private key is not
protected, through Web Service client, the user can use the X.509
certificate to access Grid Service or Web Service from any kind of
middleware. If the private key is protected, the can use the X.509
certificate to generate a proxy certificate (by using command-line
interface utility such as \textit{grid-proxy-init},
\textit{voms-}\textit{proxy-init}, or \textit{arcproxy}), and then use
the proxy certificate to access Grid Service or Web Service.

@@

\ \ \ \ The obvious benefit of SLCS service is that: If a user passes
the authentication to his home Identity Provider, he can get the X.509
credential at anywhere only by running the SLCS client command together
with inputing his username and password to this home IdP, and then
access the grid system conveniently; meanwhile, thanks to the single
sign-on characteristic of SAML2.0 SSO profile which is discussed in
Section 3.1, this user doesn{\textquotesingle}t not need to input his
username and password in a valid period after the first time he
succeeds to authenticate against his home IdP by running the SLCS
client command on the same node, even if this SLCS client command is
supposed to run against a few SLCS services to get a few SLCS
credentials.

@@

\ \ \ \ The delegation of credentials proposed in Grid Security
Infrastructure (GSI) is a good solution for the supporting of single
sign-on for users, except the coupling of the GSI communication which
is not so widely accepted in Web Service applications. In the design of
the new version ARC middleware, we keep the credential delegation idea,
while utilizing the SOAP communication (and TCP or TLS for transport
level communication) instead of the GSI communication for the
credential delegation process.

\ \ \ \ As shown in Figure 4, there is a specific WS client and Web
Service for processing delegation: delegation client, and delegation
service. The \textit{WSDL}(Web Service Description Language) of
delegation service has two main operations, one for processing the
delegation initiation, and \ the other for storing the signed proxy
certificate. The delegation process is detailed in Figure 5.

\ \ \ \ For the delegation process, the delegation WS client
functionality (inside each delegation service or the initial client)
which is included to access the target delegation service (d1 or d2 in
Figure 4), should use the user{\textquotesingle}s X.509 credential or
delegated credential (on behalf of the user) for authentication and
secure communication, as well as delegating one more level of delegated
credential. For other general \ service invocation process, the WS
client functionality (inside each service or the initial client) which
is included to access the target service (step a1 or a2 in Figure 4),
should also use the user{\textquotesingle}s X.509 credential or
delegated credential (on behalf of the user) for authentication and
secure communication.

@@

\begin{center}
\includegraphics[width=3.0638in,height=1.7827in]{Secpaper-img5.png}
\end{center}
{\centering
Figure 5. Credential delegation process
\par}

@@

\ \ \ \ WS-Security related specifications are implemented in ARC as
\textit{SecHandler}. There are three kinds of WS-Security version 1.1
specifications which are completely or partly implemented: Username
Token profile, X.509 Token profile, and SAML Token profile.

@@

\liststyleLvi
\begin{enumerate}
\item Transport level communication between delegation client and
service is not based on mutual authentication between proxy certificate
and service certificate, instead, it is based on mutual authentication
between service certificate and service certificate.
\item Delegation service will not generate any certificate request,
instead, the delegation client will pick the public key from peer
certificate after successful SSL/TLS authentication. So \ step2 of the
delegation protocol will only be some confirmation information which
lets delegation client to proceed. 
\item For those multiple intermediate services through which a SOAP
message flows, delegation service does not need to appear, instead, it
only need to appear on the end of the SOAP message flow.
\item SAML Token might include one or a few
{\textless}\textit{saml:Attribute}{\textgreater} which carries the
attribute information related to the subject, instead of the Attribute
Certificate which is used in VOMS proxy certificate for carry the
attribute information.
\end{enumerate}
\ \ \ \ Figure 7 shows the SAML Token (SAML Assertion) inside SOAP
message is changed due to delegation (we suppose X.509 token is used
for attesting entity to authenticate against issuing authority). The
SOAP message on the left side is the one which B sends to relying party
(intermediate service), B is the identity of the attesting
entity{\textquotesingle}s X.509 token, while A is the identity of
issuing authority, and the SOAP message is signed by
B{\textquotesingle}s private key which is corresponding to the X.509
certificate that is used to create the X.509 token. On the right side,
C is the identity of the delegation service (also C is the identity of
the target service to which B will access), and now the SOAP message is
signed by C{\textquotesingle}s private key which is corresponding to
the target service{\textquotesingle}s certificate.

\ \ \ It is worth mentioning is: since the SLCS X.509 credential or
delegated credential can be used to issue X.509 token, \ the X.509
credential delegation and SAML Token delegation are smoothly bridged,
which benefits the single sign-on.

@@

\begin{center}
\includegraphics[width=4.0016in,height=2.639in]{Secpaper-img6.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img7.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img8.png}
\end{center}
{\centering
Figure 6. SAML Token delegation service
\par}

@@

Similar work that integrates Shibboleth and Grid middleware does exist.
GridShib[17][18] uses Shibboleth to get entity{\textquotesingle}s
attribute for the authorization of services developed in Globus Tookit.
Unlike the work of this paper, GridShib does not use
Shibboleth{\textquotesingle}s native login handlers for authentication
to Shibboleth IdP, instead, a new login handler specific for X.509
based authentication is developed for Shibboleth IdP, and a credential
service is developed for acting as an online-CA, authenticating the
user, and issuing short-lived X.509 credential. Moreover, this paper
provides a single sign-on solution for user authenticating to Grid
services by directly using SAML2.0 SSO profile (section 3.1).

SWITCH short-lived credential service (SLCS) [19] provides a SLCS
service and client. The benefit of our work comparing to the
SWTCH{\textquotesingle}s solution is the SLCS service and client is
based on Web Service, so that it can be implemented in any Web Service
container while keeping interoperability.

In terms of delegation, apart from the credential delegation mechanism
from GSI [2][20], [21] proposes a delegation protocol based on the
WS-Trust [22] in order to provide a standard and interoperable protocol
for delegation in Grids. WS-Trust will also be adopted by ARC
middleware to express the specifications required to define delegation
protocol in a standard way. Gridsite implements a X.509 credential
delegation solution [23] based on Web Service, with which ARC
delegation client can easily interoperate.

GSI plug-in for gSOAP[24] adds GSI support for gSOAP Web Service tookit.
The GSI MCC implemented in ARC can also achieve the same functionality
as this plug-in. Moreover, the ARC solution is more flexible than it,
because GSI MCC of both service and client sides are pluggable, which
means service and client developer of ARC do not need to modify the
service or client implementation in order to add or replace the GSI
functionality.

>>>>

{\centering
Weizhong Qiang 1, Aleksandr Konstantinov 1,2 
\par}

{\centering
1University of Oslo, Department of Physics, P.O. Box 1048, Blindern,
0316 Oslo, Norway
\par}

{\centering
2Vilnius University, Institute of Material Science and Applied Research,
Sauletekio al. 9, Vilnius 2040, Lithuania 
\par}

@@

Keyword: single sign-on, delegation, virtual organization, ARC

\liststyleLi
\begin{enumerate}
\item[] {\centering
1. Introduction
\par}
\end{enumerate}
\ \ \ \ Grid provides the technology for wide-scale, cross-domain
collaboration where the users work on resources and sharing data which
are distributed across domains. This kind of collaboration is called
virtual organization (VO)[1]. The resources that contribute to the VO
could come from independent administrative domains, and even require
different security approaches for control the access to themselves
because different middlerwares are used as platform. The same
heterogeneous situation applies to users who need to access the VO,
because users holding one kind of credential could need to travel
through multiple resources with different security approaches. To solve
the above issues, the Grid middlewares should provide the following
ability:

\liststyleLii
\begin{itemize}
\item The user which participates the VO should be able to access data
and resources without being required to constantly do authentication at
each resource or data; 
\item The VO should be able to easily manage the privileges or
memberships of the users; 
\item The VO together with its resources should be able to easily manage
the authorization, given the condition that the resources are owned by
different administrative domains.
\end{itemize}
\ \ \ \ In grid community, Grid Security Infrastructure (GSI)[2] is the
\textit{de facto} for authentication and \ transport level
communication, which builds on Public Key Infrastructure (PKI), an
architecture based on X.509 public key certificate. GSI implements some
enhancement (such as certificate delegation) based on standard SSL/TLS
protocol. Mutual authentication is required by GSI, and is the default
configuration for GSI based grid deployment. The X.509 certificates are
required for both the client and service sides in order to achieve
mutual authentication. The X.509 certificates are issued by trusted
third parties called certificate authorities (CA), and then CAs
constitute trust federation and guarantee two different X.509
certificates from different CAs can accomplish authentication to each
other. So in the GSI based Grid system, if a user would access Grid
system, he/she should own a X.509 certificate which is issued by a CA
that is trusted by other entities.

\ \ \ \ In terms of the virtual organization issues mentioned earlier,
GSI and some other related solutions like Virtual Organization
Management Service (VOMS) [3] have partly solved them in some sense.
The identity delegation and X.509 proxy certificate initiated by GSI
can achieve single sign-on, so that the need to re-enter the
user{\textquotesingle}s pass phrase for authentication can be avoided
by creating the proxy certificate. \ As the most successful Grid
authorization model, VOMS adopts Attribute Certificate[4] approach.
Attribute Certificate is signed by VOMS server and then binded to proxy
certificates by client, \ and attributes certificate includes the VO
memberships which is associated with the proxy
certificate{\textquotesingle}s identity. Eventually the resources can
make access control decision based on parsing the VO membership
attributes from the Attribute Certificate.

@@

\liststyleLiii
\begin{itemize}
\item The GSS API based confidential communication has not been adopted
by Web Service implementations.
\item The Attribute Certificate has not been adopted by any Web Service
implementation at all.
\item Web Service implementations commonly use the Web Services
Security(WS-Security)[8], Security Assertion Markup Languages
(SAML)[9], and standard SSL/TLS as well as standard X.509 certificate
when considering security, which make them impossible to interoperate
with the GSI based Grid middlewares.
\item Finally, identity delegation is a good solution for user or
user{\textquotesingle}s delegatee (on behalf of the user) to
move/travel from one resource to another resource. But since the
identity delegation has been completely coupled with the GSI
confidential communication process, it is not possible for the existing
identity delegation solution to be used by Web Service applications.
\end{itemize}
\ \ \ \ Moreover, the grid security solutions require each user to
possess a X.509 certificate. But the process to get a certificate may
take quite long time, since the requester needs to be checked and
approved by the Registration Authority (RA) and then the Certificate
Authority (CA) can issue the certificate according to the approval from
RA. Meanwhile the process to use the certificate is also not so easy
for the wider less-IT focused research community to deal with, since
the user need to generate the proxy certificate by using the grid
specific command lines, such as \textit{grid-proxy-init}, and
\textit{voms-proxy-init}. On the other hand, users could often have
some local community/institutional credentials such as
username/passwords to which users are more familiar. Enabling users to
use their own community credential instead of the X.509 certificate to
access Grids is a promising solution to make the Grids more easily
accessible.

@@

\ \ \ \ ARC(Advanced Resource Connector) is an open source Grid
middleware solution released under Apache license. ARC middleware
initially aimed at developing self-organized, fault-tolerant,
non-intrusive, easy-manageable Grid middleware [10]. Now the classic
version of ARC provides Grid services for job submission and
management, resource characterization, resource aggregation and
discovery, basic data management, integration of grid security
solution, etc. Classic ARC has been deployed and used in production
environment, and been one of the widely deployed Grid middlewares in
Europe.

\ \ \ \ The new generation of ARC is developed by KnowARC project [11],
based on the functionality and capabilities of the classic ARC
middleware. It aims at implementing a Web Service oriented Grid
middleware which will provide higher levels of resource and user
abstraction through well-defined Web Service interface [12] in order to
provide interoperability with other service-based Grid middlewares, as
well as other Web Service compatible applications.

@@

\begin{center}
\includegraphics[width=3.528in,height=3.098in]{Secpaper-img1.png}
\end{center}

@@

\ \ \ \ HED contains a framework for implementing and enforcing
authentication and authorization. Each MCC or Service has a common
interface for implementing various authentication and authorization
functionality. Each functionality can be implemented as a pluggable and
configurable component (plug-ins) called \textit{SecHandler} which is
C++ class and provides method for processing message that travels
through MCC or Service. Each MCC or Service is usually configured with
two queues of \textit{SecHandler} -- one for incoming message and one
for outgoing message respectively. All \textit{SecHandler} components
attached to the queue are executed sequentially. If any of them fails,
message processing fails as well. In Figure 1, the
{\textquotedblleft}\textit{AuthZ}{\textquotedblright} and
{\textquotedblleft}\textit{AuthN}{\textquotedblright} sub-modules
inside MCCs and Services are examples of \textit{SecHandler}.

\ \ \ \ As explained above, HED is supposed to act as a Web/Grid Service
container, but on the client side, from implementation perspective,
there is similar architecture implemented for processing messages from
different protocols and handling security functionality, also there is
a specific application programming interface (API) for developers to
easily write Web Service client code.

@@

\liststyleLiv
\begin{itemize}
\item \textit{Integration of community authentication} -{}-{}- to
utilize the standard-compatible community authentication mechanism from
Shibboleth [14] Identity Provider software when users authenticate
against Grid services.
\item \textit{Short lived credential service} \ {}-{}-{}- to issue the
short lived X.509 certificates for users by using the community
authentication, in order to interoperate with services that depend on
PKI based mutual authentication.
\item \textit{Credential delegation service} -{}-{}- to process the
X.509 credential delegation as a normal Web Service, in order to
provide single sign-on ability.
\item \textit{Message level authentication} -{}-{}- to provide message
level authentication by implementing WS-Security.
\item \textit{SAML token delegation service} -{}-{}- to process the
delegation of WS Security SAML token in order to provide single sign-on
for SOAP message level authentication.
\end{itemize}
3.1 Community based authentication for Grid by utilizing Shibboleth
Identity Provider

@@

\ \ \ \ Shibboleth provides cross-domain single sign-on and
attribute-based authorization while preserving user privacy. It is
based on the OASIS Security Assertion Markup Language (SAML),
especially the \ new version of Shibboleth supports SAML 2.0
specification. For authentication, the main SAML profile that
Shibboleth implements is the SAML2.0 web browser SSO profile, which
\ define two functional components, an Identity Provider and a Service
Provider. The Identity Provider (IdP) is responsible for creating,
maintaining, and managing user identity, while the Service Provider
(SP) is responsible for controlling access to services and resources by
using the SAML assertion produced and issued by IdP upon request. In
order to discover which home community does a user come from,
Shibboleth specifies an optional third component called
{\textquotedblleft}Where Are You From?{\textquotedblright} (WAYF)
service to aid in the process of IdP discovery, and this IdP discovery
process is also standardized and \ defined in SAML 2.0 specification
and called as {\textquotedblleft}Identity Profile Discovery
Profile{\textquotedblright}.

@@

\liststyleLv
\begin{enumerate}
\item The client uses the user agent interface to launches a http
request including the IdP name (to which the user belongs) to the
service side. The endpoint of the SP service is the same as that of the
other target services, except the last part of the endpoint is
{\textquotedblleft}saml2sp{\textquotedblright} which is specific for
pointing to the SP Service. Note that we use Identity Provider (IdP)
name here to simplify the IdP discovery process in order to avoid the
IdP discovery process, because we suppose that user who would access
the target services should better know where is he from initially.
\item The SP Service (Service Provider) searches the metadata (we use
the same metadata format defined in Shibboleth) and gets the location
of the single sign-on service (hosted in IdP) and also the location of
assertion consuming service (hosted in this SP itself) in order to
compose the SAML {\textless}\textit{samlp:AuthnRequest}{\textgreater}
message. Then SP Service issues this
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message by using
its own X.509 certificate (Note in the SAML SSO profile, X.509
certificates are still needed for IdP and SP) and sends back to user
agent.
\item User agent sends the
{\textless}\textit{samlp:AuthnRequest}{\textgreater} message to
Identity Provider.
\item Identity Provider requires an act of authentication. The
authentication mechanism is outside of the SAML2.0 SSO profile.
Shibboleth IdP implementation chooses some login handlers for
authentication. The current user agent implementation is compatible to
\textit{Username/Password} login handler of Shibboleth IdP. Through the
http protocol, user agent will feed IdP with the username/password
which has been given by the caller of user agent interface.
\item Once the authentication has been succeeded, the IdP issues a SAML
response including an encrypted (encrypted by destination
SP{\textquotesingle}s public key) SAML assertion, and then this SAML
response will be delivered by the user agent to the Service Provider. 
\item The SP Service verifies and checks the SAML response, decrypts and
stores the SAML assertion into session/connection context. The SAML
assertion includes the
{\textless}\textit{saml:AuthnStatement}{\textgreater} and
{\textless}\textit{saml:AttributeStatement}{\textgreater}.
\item The WS client launches the Grid/Web Service request via the same
connection as the one which is used by user agent to contact SP
Service.
\item The Grid/Web Service checks the
{\textless}\textit{saml:AuthnStatement}{\textgreater} from the session
context to see if the session is still valid through the
\textit{SecHandler} called {\textquotedblleft}\textit{SAML
SecHandler}{\textquotedblright}. If valid, service handles the service
processing and returns the response to WS client. Note that service
requires that WS client is from the same connection as the one on which
user agent contact SP service, in order to guarantee that the validity
of SSO profile result effects the WS client/Web Service interaction.
\end{enumerate}
\ \ \ \ The SP service and other functional service(s) are hosted by the
same container, and they use the same X.509 credential. The client
authentication is switched off, so that client doesn{\textquotesingle}t
need to use any X.509 credential. Only the trusted certificates (CA
certificates for both SP and IdP) need to be configured for client side
so that SP and IdP can authenticate themselves to the client. As
required by SAML2.0 profile, the SP and IdP should have trust
relationship to each other.

@@

Moreover, even though the implementation is based on ARC middlerware,
the idea can be adopted by other Grid middlewares if they only require
server authentication instead of mutual authentication.

@@

\ \ \ \ Since the lifetime of the short lived credential is normally
short, it is not a must to protect the private key by pass phrase. As
illustrated in step a and step b in Figure 3, if the private key is not
protected, through Web Service client, the user can use the X.509
certificate to access Grid Service or Web Service from any kind of
middleware. If the private key is protected, he can use the X.509
certificate to generate a proxy certificate (by using command-line
interface utility such as \textit{grid-proxy-init},
\textit{voms-}\textit{proxy-init}), and then use the proxy certificate
to access Grid/Web Service.

@@

\ \ \ \ The obvious benefit of SLCS service is that: If a user passes
the authentication to his home Identity Provider, he can get the X.509
credential at anywhere only by running the SLCS client command together
with inputing his username and password to this home IdP, and then
access the grid system conveniently; meanwhile, thanks to the single
sign-on characteristic of SAML2.0 SSO profile, this user
doesn{\textquotesingle}t not need to input his username and password in
a valid period after the first time he succeeds to authenticate against
his home IdP by running the SLCS client command on the same node, even
if this SLCS client command is supposed to run against a few SLCS
services to get a few SLCS credentials.

@@

\ \ \ \ The delegation of credentials proposed in Grid Security
Infrastructure (GSI) is a good solution for the supporting of single
sign-on for users, except the coupling of the GSI communication which
is not so widely accepted in Web Service applications. In the design of
the new version ARC middleware, we keep the credential delegation idea,
while utilizing the SOAP communication (together with TCP or TLS for
transport level communication) instead of the GSI communication for the
credential delegation process.

\ \ \ \ As shown in Figure 4, there is a specific WS client and Web
Service for processing delegation: delegation client, and delegation
service. The \textit{WSDL}(Web Service Description Language) of
delegation service has two main operations, one for processing the
delegation initiation, and \ the other for storing the signed proxy
certificate. The delegation protocol is detailed in Figure 5.

\ \ \ \ For the delegation process, the delegation WS client
functionality (inside each delegation service or the initial client)
which is included to access the target delegation service (d1 or d2 in
Figure 4), should use the user{\textquotesingle}s X.509 credential or
delegated credential (on behalf of the user) for authentication and
secure communication, as well as delegating one more level of delegated
credential. For other general \ service invocation process, the WS
client functionality (inside each service or the initial client) which
is included to access the target service (step a1 or a2 in Figure 4),
should also use the user{\textquotesingle}s X.509 credential or
delegated credential for authentication and secure communication.

@@

\begin{center}
\includegraphics[width=3.0638in,height=1.7827in]{Secpaper-img5.png}
\end{center}
{\centering
Figure 5. Credential delegation protocol
\par}

@@

\ \ \ \ WS-Security related specifications are implemented as
\textit{SecHandler} in ARC. There are three kinds of WS-Security
version 1.1 specifications which are completely or partly implemented:
Username Token profile, X.509 Token profile, and SAML Token profile.

@@

\liststyleLvi
\begin{enumerate}
\item Transport level communication between delegation client and
service is not based on mutual authentication between proxy certificate
and service certificate, instead, it is based on mutual authentication
between service certificate and service certificate.
\item Delegation service will not generate any certificate request,
instead, the delegation client will pick the public key from peer
certificate after successful SSL/TLS authentication. So step2 of the
delegation protocol is only be some confirmation information which
informs delegation client to proceed. 
\item For those multiple intermediate services through which a SOAP
message flows, delegation service does not need to appear, instead, it
only need to appear on the end of the SOAP message flow.
\item SAML Token might include one or a few
{\textless}\textit{saml:Attribute}{\textgreater} which carries the
attribute information related to the subject, instead of the Attribute
Certificate which is used in VOMS proxy certificate for carry the
attribute information.
\end{enumerate}
\ \ \ \ Figure 7 shows the SAML Token (SAML Assertion) inside SOAP
message is changed due to delegation (we suppose X.509 token is used
for attesting entity to authenticate against issuing authority). The
SOAP message on the left side is the one which B sends to relying party
(intermediate service). B is the identity of the attesting
entity{\textquotesingle}s X.509 token, while A is the identity of
issuing authority, and the SOAP message is signed by
B{\textquotesingle}s private key which is corresponding to the X.509
certificate that is used to create the X.509 token. On the right side,
C is the identity of the delegation service (also C is the identity of
the target service to which B will access), and now the SOAP message is
signed by C{\textquotesingle}s private key which is corresponding to
the target service{\textquotesingle}s certificate.

\ \ \ What is worth mentioning is: since the SLCS X.509 credential or
delegated credential can be used to issue X.509 token, \ the X.509
credential delegation and SAML Token delegation are smoothly bridged,
which benefits the single sign-on.

@@

\begin{center}
\includegraphics[width=4.0016in,height=2.639in]{Secpaper-img6.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img7.png}
\end{center}
\begin{center}
\includegraphics[width=6.9252in,height=0.0161in]{Secpaper-img8.png}
\end{center}
{\centering
Figure 6. SAML Token delegation service and client
\par}

@@

\ \ \ \ Similar work that integrates Shibboleth and Grid middleware does
exist. GridShib[17][18] uses Shibboleth to get
entity{\textquotesingle}s attribute for the authorization of services
developed in Globus Tookit. Unlike the work of this paper, GridShib
does not use Shibboleth{\textquotesingle}s native login handlers for
authentication to Shibboleth IdP, instead, a new login handler specific
for X.509 based authentication is developed for Shibboleth IdP, and a
credential service is developed for acting as an online-CA,
authenticating the user, and issuing short-lived X.509 credential.
Moreover, this paper provides a single sign-on solution for user with
community credential authenticating to Grid services by directly using
SAML2.0 SSO profile.

\ \ \ \ SWITCH short-lived credential service (SLCS) [19] provides a
SLCS service and client. The benefit of our work comparing to the
SWTCH{\textquotesingle}s solution is the SLCS service and client is
based on Web Service, so that it can be implemented in any Web Service
container while keeping interoperability.

\ \ \ \ In terms of delegation, apart from the credential delegation
mechanism from GSI [2][20], [21] proposes a delegation protocol based
on the WS-Trust [22] in order to provide a standard and interoperable
protocol for delegation in Grids. WS-Trust will also be adopted by ARC
middleware to express the specifications required to define delegation
protocol in a standard way. Gridsite project implements a X.509
credential delegation solution [23] based on Web Service, with which
ARC delegation client can easily interoperate.

\ \ \ \ GSI plug-in for gSOAP[24] adds GSI support for gSOAP Web Service
tookit. The GSI MCC implemented in ARC can also achieve the same
functionality as this plug-in. Moreover, the ARC solution is more
flexible than it, because GSI MCC of both service and client sides are
pluggable, which means service and client developer of ARC do not need
to modify the service or client implementation in order to add or
replace the GSI functionality.
